\documentclass[oneside]{report}

\input{common}

\SetOrganization{Primordial Machine's}
\SetLibraryName{Arithmetic Library}
\SetLibraryVersion{v1.4}
\SetLibraryRepository{https://github.com/primordialmachine/arithmetic}
\SetAuthor{Michael Heilmann}
\SetEmail{michaelheilmann@primordialmachine.com}

\begin{document}
\maketitle
\tableofcontents
\chapter*{Synopsis}
C++ 17 library providing arithmetic functors and arithmetic errors and exceptions.
The library is made available publicly on
\href{\GetLibraryRepository}{Github}
under the
\href{\GetLibraryRepository/blob/master/LICENSE}{MIT License}.

\chapter{Limitations and Restrictions}
The library officially only supports Visual Studio 2017 and Windows 10.

\chapter{Requirements}
This library depends on the \href{https://github.com/primordialmachine/errors}{Primordial Machine's Errors Library}.

\chapter{Introductory example}
\textit{\color{orange}This library does not provide any examples yet.}
%Examples are located in the \href{\GetLibraryRepository/blob/master/examples}{examples} directory.

\chapter{Building under Visual Studio 2017}
\begin{enumerate}
\item Open the solution \texttt{solution.sln} in Microsoft Visual Studio 2017.
\item Batch build everything.
\item The folder \texttt{packages} contains the distribution of the library i.e. include files and the
      static libraries for
  \begin{enumerate}
    \item the platforms \texttt{Win32} and \texttt{x64} and
    \item configurations \texttt{Release} and \texttt{Debug}.
  \end{enumerate}
\item Copy the contents of the \verb+packages+ folder into a directory. Let
      \verb+[library home]+ be a placeholder denoting the path by which that folder
      can be referenced from your project.
\item Add
  \begin{enumerate}
    \item the include path
\begin{verbatim}
[library home]/primordialmachine/arithmetic-functors/
$(PlatformTarget.toLower())/$(Configuration.toLower())/includes
\end{verbatim}
	and
    \item the library path
\begin{verbatim}
[library home]/primordialmachine/arithmetic-functors/
$(PlatformTarget.toLower())/$(Configuration.toLower())/libraries
\end{verbatim}
    to your project.
\end{enumerate}
\item Link your project with the library \verb+arithmetic-functors.lib+.
\item Add the include directive \verb+#include "primordialmachine/arithmetic_functors/include.hpp"+ where appropriate.
\item You can now use the functionality provided by the library.
\end{enumerate}

\chapter{Library Interface Documentation}

\section{\texttt{namespace primordialmachine}}
The namespace this library is adding its declarations/definitions to.
The added namespace elements are documented below.

\section{\textit{concept BinaryFunctor}}
A \textit{BinaryFunctor} is a function object with three template arguments \verb+LEFT_OPERAND+,
\verb+RIGHT_OPERAND+, and \verb+ENABLED+. Specializations of this type must provide a
constant \verb+operator()+ with two parameters \verb+left_operand+ of type \verb+LEFT_OPERAND+
(or a cv-qualified variant of that) and \verb+right_operand+ of type \verb+RIGHT_OPERAND+
(or a cv-qualified variant of that). The return value of that operand shall represent the
result of the operation \verb+left_operand OP right_operand+ where OP is the binary operation
the \textit{BinaryFunctor} represents.\\

\noindent{}The default type of \verb+ENABLED+ is \verb+void+. Specializations of this type may use
the \verb+ENABLED+ argument to perform \textit{SFINAE}.

\section{\texttt{struct binary\_plus\_functor}}
A \textit{BinaryFunctor} representing the binary operation \verb|left_operand + right_operand|.
This library provides specializations for \texttt{LEFT\_OPERAND} and \texttt{RIGHT\_OPERAND} being floating point types.

\section{\texttt{struct binary\_minus\_functor}}
A \textit{BinaryFunctor} representing the binary expression \verb|left_operand - right_operand|.
This library provides specializations for \texttt{LEFT\_OPERAND} and \texttt{RIGHT\_OPERAND} being floating point types.

\section{\texttt{struct binary\_star\_functor}}
A \textit{BinaryFunctor} representing the binary expression \verb|left_operand * right_operand|.
This library provides specializations for \texttt{LEFT\_OPERAND} and \texttt{RIGHT\_OPERAND} being floating point types.

\section{\texttt{struct binary\_slash\_functor}}
A \textit{BinaryFunctor} representing the binary expression \verb|left_operand / right_operand|.
This library provides specializations for \texttt{LEFT\_OPERAND} and \texttt{RIGHT\_OPERAND} being floating point types.

\section{\textit{concept UnaryFunctor}}
A \textit{UnaryFunctor} is a function object with two template arguments \verb+LEFT_OPERAND+,
\verb+RIGHT_OPERAND+, and \verb+ENABLED+. Specializations of this type must provide a
constant \verb+operator()+ with one parameter \verb+operand+ of type \verb+OPERAND+
(or a cv-qualified variant of that). The return value of that operand shall represent the
result of the operation \verb+OP operand+ where OP is the unary operation
the \textit{UnaryFunctor} represents.\\

\noindent{}The default type of \verb+ENABLED+ is \verb+void+. Specializations of this type may use
the \verb+ENABLED+ argument to perform \textit{SFINAE}.

\section{\texttt{struct unary\_plus\_functor}}
A \textit{UnaryFunctor} representing the unary expression \verb|+operand|.
Ths library provides specializations for \texttt{OPERAND} being a floating point type.

\section{\texttt{struct unary\_minus\_functor}}
A \textit{UnaryFunctor} representing the unary expression \verb|-operand|.
This library provides specializations for \texttt{OPERAND} being a floating point type.

\section{\texttt{division\_by\_zero\_error}}
An error (as specified in Primordial Machine's Errors library) indicating a division by zero.

\section{\textit{concept Error}}
\textit{\color{orange}This section needs to be moved in Primordial Machine's Error library.}
\noindent\textit{\color{orange}[[}\\
An \textit{Error} type is a \texttt{error} or derived type.\\
\noindent\textit{\color{orange}]]}

\section{\textit{concept Exception}}
\textit{\color{orange}This section needs to be moved in Primordial Machine's Error library.}
\noindent\textit{\color{orange}[[}\\
An \textit{Exception} type is a \texttt{exception} or derived type.
Such an object must retain the properties of being
\begin{enumerate}
  \item noexcept copy/move constructible and
  \item noexcept copy/move assignable.
\end{enumerate}
\noindent\textit{\color{orange}]]}

\section{\texttt{negative\_overflow\_error}}
An \textit{Error} type (as specified in Primordial Machine's Errors library) indicating a negative overflow.
It raises its corresponding \texttt{negative\_overflow\_exception}.
The term negative overflow refers to the situation in which an arithmetic value is non-positive and
too big (in terms of its magnitude) to be represented. Its constructor takes a single argument which
is a \texttt{error\_position} value.

\section{\texttt{positive\_overflow\_error}}
An \textit{Error} type (as specified in Primordial Machine's Errors library) indicating a positive overflow.
It raises its corresponding \texttt{negative\_overflow\_exception}.
The term positive overflow refers to the situation in which an arithmetic value is non-negative and
too big (in terms of its magnitude) to be represented. Its constructor takes a single argument which
is a \texttt{error\_position} value.

\section{\texttt{underflow\_error}}
An \textit{Error} type (as specified in Primordial Machine's Errors library) indicating an underflow.
It raises its corresponding \texttt{underflow\_exception}.
The term underflow refers to the situation in which an arithmetic value is too small (in terms of
its magnitude) to be represented. Its constructor takes a single argument which
is a \texttt{error\_position} value.

\end{document}
